Measuring Political Freedom Around the World

### 2020-11-11 slides.Rmd
added meeting additions

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_slide_tone()
```

# Outline

@@

* study political freedom as a function of social, economic, political factors

@@

* From Data provided by the Gapminder Foundation.

@@

* filtered to only include OECD Countries from year 2000 to 2018

# Define political freedom

* Freedomhouse index

@@

---
# Best Subsets
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, model) %>% 
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
```
---

class: center
### Best Subsets
```{r, message=FALSE, warning=FALSE, fig.align='center', fig.width=12, fig.height=8}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

@@

>>>>

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE) 
```

# Research Question

@@

* Observational study of political freedom as a function of social, economic, political factors.

--
* From Data provided by the Gapminder Foundation.

@@

* filtered to only include OECD Countries from year 2000 to 2018 by necessity

@@

# Political Freedom

@@

* covarites w/ exp

# Summary Stats

# Assumptions

--
* Finite mean and sd
* independance
* Linearity
* Normaily
* Homoskidasticity

# Best Subsets
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, model) %>% 
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
```

class: center

```{r, message=FALSE, warning=FALSE}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

@@

---
# Remedial measured

* plot
* 
* vif
car::vif(fit)

* Brown Forsythe

---
# Conclusions
